\cvsection{Finance Projects}
\begin{cventries}
  \cventry
    {(Intern)Asset management assistant for quantified financial product research}
    {Chongqing International Trust}
    {Wuxi, China}
    {July. 2021}
    {
      \begin{cvitems}
        \item {Conducted in-depth risk assessments influenced by macroeconomic policies, optimizing investment security}
        \item {Evaluated consumer investment strategies through data-driven research, adapting to diverse economic scenarios}
        \item {Streamlined analysis and validation of Snowball derivatives employing Monte Carlo simulations for knock-in/out options, enhancing accuracy and efficiency}
      \end{cvitems}
    }

  \cventry
    {(Intern)Investment assistant for tech industry research and investment strategies}
    {Addor Capital}
    {Nanjing, China}
    {May. 2021 - Jun. 2021}
    {
      \begin{cvitems}
        \item {Conducted, transcribed, and evaluated in-person and virtual interviews, presenting key insights to stakeholders}
        \item {Assessed potential fraud risks pre-financial due diligence through comprehensive research, mitigating financial exposure}
        \item {Measured and assessed Cyber Range industry performance employing DCF and linear regression methodologies, driving strategic decision-making}
      \end{cvitems}
    }

  \cventry
    {Data preprocessing and analysis with Arnav Sheth and Gita Rao(MIT Sloan)}
    {ESG fund voting pattern research(published)}
    {Remote}
    {Feb. 2021 - Mar. 2021}
    {
      \begin{cvitems}
        \item {Developed a multi-threaded web crawler for extracting voting records from the SEC EDGAR database, leading to faster data acquisition and reduced processing time}
        \item {Implemented a universal data pipeline using regular expressions for accurate filtering and analysis, streamlining the data processing workflow and enhancing output quality}
      \end{cvitems}
    }
  
  \begin{comment}
  \cventry
    {Consultant}
    {Consulting with Frauenmond, TBM Inc.}
    {Seoul, Korea}
    {Oct. 2019 - Dec. 2019}
    {
      \begin{cvitems}
        \item {Analyzed Korean chocolate market with Porter's Five Forces Model and managerial accounting}
        \item {Strategized with Encouragement Study based on Genetic Matching and Regression Discontinuity}
        \item {Offered Neural Network model for Alpha/Beta tests on feature designing}
      \end{cvitems}
    }

  \cventry
    {Group leader \& Coder}
    {Complex Network at the University of Pennsylvania}
    {Philadelphia, United States}
    {Jul. 2016 - Aug. 2016}
    {
      \begin{cvitems}
        \item {Analyzed social/bio network with stochastic simulation}
        \item {Implemented PageRank under a distribution network setting}
        \item {200x speedup in a month's iteration}
      \end{cvitems}
    }

  \cventry
    {Image Analyzer \& Asteroid Researcher}
    {IASC Asteroid Search}
    {Wuxi, China}
    {Jun. 2015 - Oct. 2015}
    {
      \begin{cvitems}
        \item {Analyzed images for possible unidentified asteroid with image recognizing algorithm}
        \item {Reported results to Minor Planet Center, Harvard University}
        \item {Located 2 asteroids based on NASA-provided images}
      \end{cvitems}
    }
    \end{comment}
\end{cventries}
