\cvsection{Tech experiences}
\begin{cventries}

  \cventry
    {ZGC Lab - State Key Laboratories}
    {(Research) Secuirty-in-design high performance macro kernel}
    {Beijing, CN}
    {2024 - PRESENT}
    {
      \begin{cvitems}
        \item {Redesigned Linux compartmnetalization, realizing user space protection and hardware isolation}
        \item {Implemented SFI-based eBPF isolation for data structure protection with JIT instrumentation}
        \item {Porting Linux-based hardening techniques to OpenKylin and OpenEuler OS}
      \end{cvitems}
    }

  \cventry
    {Brown Secure Systems Lab}
    {(Research) SysXCHG: a dynamic Linux kernel filter for system calls}
    {Providence, US}
    {Jan. 2023 - PRESENT}
    {
      \begin{cvitems}
        \item {Developed an advanced log-time syscall filtering application using seccomp BPF, resulting in improved system efficiency}
        \item {Customized Linux kernel 6.0.8 compilation, integrating arity-based filters for enhanced performance}
        \item {Designed comprehensive test suites, leading to the attainment of the 2023 CCS Functional Badge}
      \end{cvitems}
    }
  
  \cventry
    {Zhejiang University(advisor: Wenbo Shen)}
    {(Research) Interp-flow Hijacking: Non-control Data Attack via Hijacking eBPF Interpretation Flow} 
    {Providence, US}
    {Sep. 2023 - PRESENT}
    {
      \begin{cvitems}
        \item {2024 Distingished Paper Award at ESORICS}
        \item {A novel method to hijack eBPF interpretation flow, increasing kernel attack capability}
        %\item {Edited, reviewed, and proofread the paper before submission, ensuring quality and accuracy}
        \item {Conducted comprehensive background research in the areas of eBPF and kernel security}
      \end{cvitems}
    }


  \cventry
    {Brown University}
    {(Research) Microservice benchmarking}
    {Providence, US}
    {Sep. 2023}
    {
      \begin{cvitems}
        \item {Analyzing and evaluating microservice frameworks employed by Meta and Alibaba}
        \item {Designing a realistic data pipeline for microservice benchmarking}
      \end{cvitems}
    }

  \cventry
    {Bank of America}
    {(Internship) Data automation and Security}
    {Charlotte, US}
    {May. 2023 - Aug. 2023}
    {
      \begin{cvitems}
        \item {Implemented testing coverage through streamlining protocols, leading to 25\% time savings}
        \item {Visualized coverage statistics through Python and Alteryx, delivering analysis to senior directors}
        \item {Developed high-concurrency data workflows for SQL and NoSQL databases}
      \end{cvitems}
    }

  \begin{comment}
  \cventry
    {Machine Learning \& Computation}
    {Chemical Molecular Energy Optimization}
    {Providence, RI}
    {Aug 2022 - Present}
    {
      \begin{cvitems}
        \item {Analyzed traditional Hartree-Fock and DFT methods with Gaussian}
        \item {Implemented the original data pipeline on Brown's Oscar super computing cluster with 200x speed}
        \item {Working on an efficient Belief Propagation network based on HMC}
      \end{cvitems}
    }
  \end{comment}

  \cventry
    {Elle Investments}
    {(Internship)Full stack trading data solution}
    {Remote, US}
    {May. 2022 - Dec. 2022}
    {
      \begin{cvitems}
          \item {Overhauled a low-level persistent storage saving 20\% write time, 40\% read time, and 45\% RAM, increasing overall performance}
          \item {Addressed SQL injection vulnerabilities and restructured MVC+OOP stateless deployment framework to strengthen security measures}
          \item {Implemented a dynamic HTTP cache that increased concurrency by 1000x, significantly enhancing the overall user experience}
      \end{cvitems}
    }
  %% \cventry
  %%   {Reverse engineering}
  %%   {ILCE SLR camera RPC}
  %%   {Remote}
  %%   {Dec 2021}
  %%   {
  %%     \begin{cvitems}
  %%       \item {Web traffic analysis for hidden access point}
  %%       \item {Designed object-oriented camera API for user interaction}
  %%       \item {Developed iPhone widget for remote camera operation}
  %%     \end{cvitems}
  %%   }

  \cventry
    {The IBM Qiskit Quantum Computing}
    {(Research) Quantum machine learning lab}
    {Remote}
    {July 2021 - Aug. 2021}
    {
      \begin{cvitems}
%        \item {Achieved 100\% in implementing diverse Quantum Machine Learning algorithms on IBM Quantum platform}
        \item {Investigated practical applications of Quantum Approximate Optimization Algorithm, optimizing solutions for complex problems}
        \item {Conducted in-depth analysis of Quantum Boltzmann Machines, driving advancements in data generation and quantum computing}
      \end{cvitems}
    }

  \begin{comment}
  \cventry
    {Correlation between Fama-French factors and business cycles}
    {(Research) Timing strategy based on spread curve inversion, second author}
    {Remote}
    {June 2021 - PRESENT}
    {
      \begin{cvitems}
        \item {Advised by Dr. Arnav Sheth from MIT}
        \item {Developed a probit-based recession forecasting model, achieving 70\% accuracy, which contributed to a 10\% annualized return}
        \item {Analyzed business cycles through Fama-French factors using ex-ante and ex-post evaluation methods, confirming the model's validity}
      \end{cvitems}
    }

  \cventry
  {Full-stack development for an event-driven quantitative trading simulation}
  {Quantitative trading PaaS}
  {Remote}
  {Sep. 2020 - PRESENT}
  {
    \begin{cvitems}
      \item {Implemented benchmark tools based upon ARIMA and Prophet}
      \item {Designed UI\&UX with quantified alpha/beta testing, improving user experience}
      \item {Proposed low latency APIs that allow high frequency trading via HTTP}
    \end{cvitems}
  }
  
  \cventry
    {(Internship)Project manager \& developer for a change detection model on VHR satellite pictures}
    {Shunzhi Tech Inc.}
    {Nanjing, China}
    {Jun. 2020 - Sep. 2020}
    {
      \begin{cvitems}
        \item {Implemented real-time video stream object detection framework with 34\% improvement than benchmark}
        \item {Deployed results to heterogeneous computing units from multiple service providers, saving 20\% cost}
      \end{cvitems}
    }

  
  \cventry
    {Project manager \& Coder}
    {Project Safe Francisco with Gensler Inc.}
    {San Francisco, United States}
    {Sep. 2018 - May. 2019}
    {
      \begin{cvitems}
        \item {Developed a San Francisco simulation game, chosen as showcase project}
        \item {Scripted game events based on interviews and surveys}
        \item {Continuous intergration with Gensler Inc. and their architecture designing team}
      \end{cvitems}
    }
  \cventry
    {Literature review \& Data analysis}
    {Re-examine recessional velocity based upon a `variable' Hubble constant}
    {San Francisco, United States}
    {Nov. 2018}
    {
      \begin{cvitems}
        \item {Provided a unified framework for existing theories and explanations}
        \item {Quantified recessional velocity index using linear regression}
      \end{cvitems}
    }

  \cventry
    {Data collection \& Analysis}
    {San Francisco rising sea level monitoring and prognosis}
    {San Francisco, United States}
    {Dec. 2018}
    {
      \begin{cvitems}
        \item {Extensively sampled sea level and ecological data along San Francisco coastline}
        \item {Validated results with ex ante probit model based upon historical data}
        \item {Performed a case study with SFO's designers on city planning}
      \end{cvitems}
    }
 

  \cventry
    {Web developer \& Component designer}
    {Nine Chapter Inc.}
    {Shanghai, China}
    {Aug. 2017 - Nov. 2017}
    {
      \begin{cvitems}
        \item {Streamlined frontend building process}
        \item {20x speedup for project building with caching design}
        \item {Bridged major front-to-back communications \& REST API design}
      \end{cvitems}
    }
  \end{comment}
  
\end{cventries}
